---
title: "homework 3"
format: docx
editor: visual
---

```{r}
library(tidyverse)
library(here)
library(flextable)
library(janitor)
library(dplyr)
```

### A.

I could calculate the central tendencies for walking pace for both categories of shoe that I wear (docs or sneakers) to see if my shoes affect my walking pace. I think that docs make me walk slower since they are less comfortable.

### B.

```{r}
my_data <- read.csv("data/my_data.csv") #reading in data

ggplot(data = my_data, #setting data frame to my_data
       aes(x = Type_of_Shoe, #setting x axis to type of shoe
           y = Pace,
           fill = Type_of_Shoe)) + #setting y axis to pace
     scale_fill_manual(values=c("#FF9FE5", "#2B50AA")) + 
  geom_boxplot() + #creating a box plot
    geom_jitter(width = 0.2,
                height = 0) +
    labs(x = "Type of Shoe", #labels for x and y axis
         y = "Pace (mm:ss)")
```

### C.

**Figure 1. Wearing docs tends to slow down walking pace.** Points represent observations of walking pace (mm:ss) for docs (n = 9) and for sneakers (n = 16). Box plots represent the central tendencies of the data and each point represents an observation of walking pace. The color represents the type of shoe (pink: docs, blue: sneakers).

### D.

```{r}
data_summary <- my_data |> 
  group_by(Type_of_Shoe) |> 
  summarise(
    median = round(median(Pace), digits = 1),
    minimum = round(min(Pace), digits = 1),
    maximum = round(max(Pace), digits = 1),
    IQR = round(IQR(Pace), digits = 1)
  )
ft <- flextable(data_summary) #creating table from my_data and storing it as an object called ft
ft <- set_caption(ft, caption = "Walking Pace in Docs vs Sneakers")
ft <- set_header_labels(ft,
                        median = "Median (min)",
                        minimum = "Minimum (min)",
                        maximum = "Maximum (min)",
                        IQR = "IQR (min)",
                        Type_of_Shoe = "Type of Shoe")
ft <- theme_box(ft)
ft
```


#### Problem 2.

### A.

An affective visualization for my data could be a drawing of each shoe that I was wearing for each observation. These shoe drawings would be distributed on the page to show the walking pace for that observation. This could be done by drawing a finish line and drawing shoes with a faster pace closer to the line and shoes that resulted in a slower pace further from the line.

### B.

