---
title: "homework 3"
format: docx
editor: visual
---

```{r}
library(tidyverse)
library(here)
library(flextable)
library(janitor)
```

### A.

I could calculate the central tendencies for walking pace for both categories of shoe that I wear (docs or sneakers) to see if my shoes affect my walking pace. I think that docs make me walk slower since they are less comfortable.

### B.

```{r}
my_data <- read.csv("data/my_data.csv") #reading in data

ggplot(data = my_data, #setting data frame to my_data
       aes(x = Type_of_Shoe, #setting x axis to type of shoe
           y = Pace,
           fill = Type_of_Shoe)) + #setting y axis to pace
     scale_fill_manual(values=c("#FF9FE5", "#2B50AA")) + 
  geom_boxplot() + #creating a box plot
    geom_jitter(width = 0.2,
                height = 0) +
    labs(x = "Type of Shoe", #labels for x and y axis
         y = "Pace (mm:ss)")
```

### C.

**Figure 1. Wearing docs tends to slow down walking pace.** Points represent observations of walking pace (mm:ss) for docs (n = 9) and for sneakers (n = 16). Box plots represent the central tendencies of the data and each point represents an observation of walking pace. The color represents the type of shoe (pink: docs, blue: sneakers).
